Improved Bounds for Online Balanced Repartitioning

### 2020-04-24 paper/disc20clustering.tex
Comments

\newcommand\mahmoud[1]{\color{green}\textbf{\\ Mahmoud: #1}\\\color{black}}
\newcommand\stefan[1]{\color{blue}\textbf{\\ Stefan: #1}\color{black}}
\newcommand\maciek[1]{\color{brown}\textbf{\\ Maciek: #1}\color{black}}
%\newcommand\maciek[1]{}

@@

Missing:
\maciek{Reason that the cost sharing between cases C1 and C3 is possible. Unclear to me, why every time C3 happens there must be a corresponding C1. \mahmoud{done}}
\maciek{Missing the case of the first-time collocation. What if t' does not exist? What if t'' does not exist? 
\mahmoud{added remark for this case: $t''=0$}}

@@

Tiny:
\maciek{$\sigma_t$ undefined (I know what it is, though). \mahmoud{added inline def. Do we have a global def for this?}}
\maciek{Define $C^t$ to use once \mahmoud{already defined! I don't get it.}}
\maciek{A word "Obviously" is unnecessary, and most people, including me are allergic to it in writing
\mahmoud{obviously that's true!}}

>>>>

\newcommand\mahmoud[1]{\color{orange}\textbf{\\ Mahmoud: #1}\\\color{black}}
\newcommand\stefan[1]{\color{blue}\textbf{\\ Stefan: #1}\color{black}}
\newcommand\maciek[1]{\color{brown}\textbf{\\ Maciek: #1}\color{black}}
%\newcommand\maciek[1]{}

@@

Missing:
\maciek{Missing the case of the first-time collocation. What if t' does not exist? What if t'' does not exist? 
\mahmoud{added remark for this case: $t''=0$}}
\maciek{But t' might not exist (as it might be the first collocation).}

@@

Tiny:
\maciek{$\sigma_t$ undefined (I know what it is, though). \mahmoud{added inline def. Do we have a global def for this?}}
\maciek{Not yet, but we still must write the "Problem definition" section (yes, we don't have one!), and we can put it there.}

\maciek{Define $C^t$ to use once \mahmoud{already defined! I don't get it.}}
\maciek{discussed}
